% This is a personal resume made by TUSHAR JAIN 
% This was last updated on 18-12-2021

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[margin=0.25in]{geometry}
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}

\renewcommand{\maketitle}{
\begin{center}
    {\Huge\textbf{TUSHAR JAIN}} \\
    \vspace{0.1in}
    {\Large\text{B.Tech Undergraduate in Computer Science and Engineering}} \\
    \vspace{0.15in}
    {\color{RedOrange} \hrule}
    \vspace{0.15in}
    {{\faGithub} \tab \href{https://github.com/TusharJ3011}{\underline{TusharJ3011}}} \hspace{1in} {{\faLinkedin} \tab \href{https://www.linkedin.com/in/tushar-jain-9b2359201}{\underline{Tushar Jain}}}
    \hspace{1in} 
    {{\faEnvelope} \tab \href{mailto:jtushar3011@gmail.com}{\underline{jtushar3011@gmail.com}}}
    \hspace{1in} 
    {{\faPhone} \tab \text{+91 6350290184}}
    
\end{center}
}

\titleformat{\section}
{\huge}
{}
{0em}
{\bfseries\color{RedOrange}}

\titleformat{\subsection}
{\Large}
{}
{1em}
{\bfseries}


\titlespacing{\subsection}{0em}{0.5em}{0em}

\begin{document}
\maketitle
{\color{RedOrange} \hrule}
\section{Education}
\vspace{-0.35cm}
\subsection{B.Tech Computer Science and Engineering}
{{\faUniversity} \tab \href{https://www.lnmiit.ac.in/}{\underline{The LNM Institute of Information Technology}}} \hspace{0.25in}
{{\faCalendar} \tab 2020-2024} \hspace{0.25in}
{{\faMapMarker} \tab Jaipur, Rajasthan, India}
\vspace{-0.2cm}
\begin{itemize}
    \item Completed 3rd Semester
    \vspace{-0.3cm}
    \item Current GPA : 7.63
\end{itemize}

\subsection{Class 12th}
{{\faUniversity} \tab \href{https://www.vidhyanjaliacademy.com/}{\underline{Vidhyanjali Academy}}} \hspace{0.25in}
{{\faCalendar} \tab 2019-2020} \hspace{0.25in}
{{\faMapMarker} \tab Kota, Rajasthan, India}
\vspace{-0.2cm}
\begin{itemize}
    \item Final Percentage : 94.6
\end{itemize}

\section{Technical Skills}
\vspace{-0.35cm}
\subsection{Languages}
Python, HTML, CSS, JavaScript, Java, LaTeX, PHP, MIPS(Assembly Language)
\subsection{Libraries/Frameworks}
Tkinter, Flask, Request (APIs), Bootstrap, Beautiful Soup, Selenium, OpenCV
\subsection{Databases}
SQL, MySQL, SQLite
\subsection{Developer Tools}
VS Code, PyCharm, Eclipse IDE
\subsection{Operating Systems}
Windows, Linux

\section{Projects}
\vspace{-0.35cm}
\subsection{\href{https://github.com/TusharJ3011/Shop-Management-System}{\underline{Shop Management System}}}
{\faLaptop} \hspace{0.1in} Python, HTML, CSS, Bootstrap, MySQL
\vspace{-0.2cm}
\begin{itemize}
  \item It is a web-based platform to maintain the sales, employees, and available products of a store.
    \vspace{-0.3cm}
  \item It uses Flask as backend and MySQL as database and Werkzeug encoding for securing logins.
    \vspace{-0.3cm}
  \item It also sends the owner an email warning when the product goes out of stock.
\end{itemize}
\subsection{\href{https://github.com/TusharJ3011/Weather-Forecasting-App}{\underline{Weather Forecasting App}}}
{\faLaptop} \hspace{0.1in} Python
\vspace{-0.2cm}
\begin{itemize}
  \item It is a weather forecasting app which gives the present and hourly weather forecast and the astronomical data of last 3 days.
    \vspace{-0.3cm}
  \item It uses Tkinter for user-interphases and APIs for getting Geo-Location and Weather Forecast.
\end{itemize}
\subsection{\href{https://github.com/TusharJ3011/Snake-Game-}{\underline{Snake Game}}}
{\faLaptop} \hspace{0.1in} Python
\vspace{-0.2cm}
\begin{itemize}
  \item A replica of the famous Nokia Snake Game.
    \vspace{-0.3cm}
  \item It uses Turtle library for functionalities.
\end{itemize}

\section{Achievements}
\vspace{-0.35cm}
\begin{itemize}
    \item Cleared State Talent Search Examination (STSE) Rajasthan 2017.
    \vspace{-0.3cm}
    \item Cleared Pre - Regional Mathematics Examination in Kota 2019.
\end{itemize}





\end{document}
